FraCaS: 80 percent complete

### 2019-02-26 paper2018/paper.tex
oops

\providecommand\forcecenter{\multicolumn{1}{c}}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#cases & Ours     & FC & MINE & Nut  & Langpro  \\ \hline
Quantifiers  & 75          & .96  & .96    & .77  & .53  & .93  \\
             &             & \ncases{74}     &        &      &      &     \ncases{44} \\
Plurals      & 33          & .82      & .76    & .67  & .52  & .73 \\
      &          &       &     &   &   & \ncases{24} \\
Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
Adjectives   & 22          & .95 & .95    & .68  & .32  & .73 \\
             &          &  \ncases{20} &     &   &   &  \ncases{12} \\
Comparatives {\kern -1em}& 31          & .87      & .56    & .48  & .45  &  -       \\
Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
Attitudes    & 13          & .92      & .85    & .77  & .46  & .92  \\ 
    &          &       &     &   &   & \ncases {9}  \\ \hline
Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
             &             & \ncases{259}    & \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the third column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} described by \citet{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for a given section. }
  \label{tab:results}
\end{table}

>>>>

\providecommand\forcecenter{\multicolumn{1}{c}}
\providecommand\ncases[1]{{\ensuremath{^{#1}}}}
\begin{table}
  \centering
  \small
\begin{tabularx}{\columnwidth}{Xr@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r@{\,\,}r}
Section      & {\kern -2em} \#cases & Ours     & FC & MINE & Nut  & Langpro  \\ \hline
Quantifiers  & 75          & .96  & .96    & .77  & .53  & .93  \\
             &             & \ncases{74}     &        &      &      &     \ncases{44} \\
Plurals      & 33          & .82      & .76    & .67  & .52  & .73 \\
      &          &       &     &   &   & \ncases{24} \\
Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
Adjectives   & 22          & .95 & .95    & .68  & .32  & .73 \\
             &          &  \ncases{20} &     &   &   &  \ncases{12} \\
Comparatives {\kern -1em}& 31          & .87      & .56    & .48  & .45  &  -       \\
Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
Attitudes    & 13          & .92      & .85    & .77  & .46  & .92  \\ 
    &          &       &     &   &   & \ncases {9}  \\ \hline
Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
             &             & \ncases{259}    & \ncases{174}  & \ncases{174}& \ncases{174}& \ncases{89}
  \end{tabularx}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases (shown in
    the second column), the actual number of test cases attempted is
    shown below the accuracy figure, in smaller font.  ``FraCoq''
    refers to the work of \citet{bernardy_type_2017}. ``MINE" refers
    to the approach of \citet{Mineshima:2015}, ``NUT" to the CCG
    system that utilizes the first-order automated theorem prover
    \textit{nutcracker} described by \citet{bos:2008}, and ``Langpro"
    to the system presented by \citet{Abzianidze:2015}. A dash
    indicates that no attempt was made for a given section. }
  \label{tab:results}
\end{table}
